\chapter{Dispatch}

The Dispatch feature is used to record the shipping of a set of patient sample
aliquots between two repository sites where all the patients and aliquots
belong to a single study.  Aliquots from multiple patients may be included in a
dispatch.  To use the dispatch feature in BioBank2 the two sites and the study
involved must first be configured. See section 5.1 for instructions.

Prior to sending the dispatch, the administrator of the sending site must
create a Dispatch entry that records the aliquots that are part of the
shipment. After the entry is created and the shipment is ready to be sent, the
administrator must mark the entry as Sent. At this point BioBank2 displays the
shipment entry as In Transit. See section 5.3 for instructions.  Sites that
wish to send dispatches can only send aliquots that have been scan assigned to
container positions. Aliquots without a position are not allowed in a dispatch.

When receiving a dispatch, a technician with the appropriate role must Receive
and Process the dispatch entry in BioBank2. Only entries marked as In Transit
can be received and processed. A technician has the option of only marking an
entry as received and then process it at a later time. Processing of a dispatch
entry involves confirming that the aliquots recorded as sent are actually
received. See section 5.4 for instructions.  The following errors can happen
when sending a dispatch:

• The shipment never arrives at the destination site.
• One or more aliquots marked as sent are not actually received at the receiving site,
• One or more aliquots never marked as sent are received at the receiving site.

Please see sections 5.5, 5.6 and 5.7 for instructions on how to deal with these
cases.  If a repository site no longer sends dispatches, the instructions to
remove the dispatche information is given in section 5.2.

\section{Configure Site for Sending Dispatches}
\section{Configure a Site to No Longer Send Dispatches}
\section{Sending a Dispatch}
\section{Receiving a Dispatch}
\section{Dispatch Never Arrives at Destination Site}
\section{Dispatches with Missing Aliquots}
\section{Dispatch with Extra Aliquots}
